Artin Group Presentations Arising from Cluster Algebras

### 2014-09-08 Paper.tex
Small Change

Throughout the section we will fix a diagram of finite type $\Gamma$, a vertex $k$ of $\Gamma$, and write $\Gamma^{\prime} = \mu_k(\Gamma)$.  We will write $s_i$, $r_i$, $q_i$, and $u_i$ for the generators corresponding to vertex $i$ of $A_{\Gamma}$, $A_{\Gamma^\prime}$, $A_{\Gamma^{op}}$, and $A_{\left(\Gamma^\prime\right)^{op}}$, respectively. Note that the $u_i$ are generators $A_{\left(\Gamma^{op}\right)^\prime}$ as well, since $\left(\Gamma^\prime\right)^{op} = \left(\Gamma^{op}\right)^\prime$.  In order to distinguish the relations in the groups $A_{\Gamma}$ and $A_{\Gamma^{\prime}}$, we shall refer to the relations on $A_{\Gamma}$ as $(T2),(T3)$ and the relations on $A_{\Gamma^\prime}$ as $(T2^\prime),(T3^\prime).$ In the proof of Theorem \ref{thm:main} we will use Lemma \ref{lem:op_homomorphism} along with the following proposition, which we prove in Section \ref{sec:proof_of_ti_relations}.

>>>>

Throughout the section we will fix a diagram of finite type $\Gamma$, a vertex $k$ of $\Gamma$, and write $\Gamma^{\prime} = \mu_k(\Gamma)$.  We will write $s_i$, $r_i$, $q_i$, and $u_i$ for the generators corresponding to vertex $i$ of $A_{\Gamma}$, $A_{\Gamma^\prime}$, $A_{\Gamma^{op}}$, and $A_{\left(\Gamma^\prime\right)^{op}}$, respectively. Note that the $u_i$ are generators $A_{\left(\Gamma^{op}\right)^\prime}$ as well, since $\left(\Gamma^\prime\right)^{op} = \left(\Gamma^{op}\right)^\prime$. In the proof of Theorem \ref{thm:main} we will use Lemma \ref{lem:op_homomorphism} along with the following proposition, which we prove in Section \ref{sec:proof_of_ti_relations}.
